### 2015-03-13 doc/notebook/2015-02-26_Bacterial_data_acquisition.Rmd
Add main heading
Make precluster file name specific to bacteria

@@

#need to make the taxonomy file match the fasta and names files...
cut -f 1 *ster.names > precluster.accnos
mothur "#get.seqs(taxonomy=all_bacteria.taxonomy, accnos=precluster.accnos)"
```

>>>>

# Getting the bacterial sequence data and metadata

@@

#need to make the taxonomy file match the fasta and names files...
cut -f 1 all_bacteria.filter.unique.precluster.names > precluster.accnos
mothur "#get.seqs(taxonomy=all_bacteria.taxonomy, accnos=precluster.accnos)"
```
